\textsc{DEVS Ex Machina} \\ Performance Report

### 2015-05-24 manual/tex/controller.tex
Additions to manual Performance report

	The default is \emph{Classic DEVS}
\\\\
\end{tabular}
\\
\begin{tabular}{lp{8cm}}
\textit{coreAmount} & The amount of cores the simulation will run on \newline
						\textit{[This option is disregarded if you do not run PDEVS]} \newline
						By default this is 1
\\\\
\textit{saveInterval} & This value decides how often the simulation is saved and the tracing output dumped. A value of 3 would mean that this happens every 3 simulation cycles. \newline
						The default value is 5
\\\\
\textit{allocator} & By default this is the included \textsl{SimpleAllocator}
\\\\
\end{tabular}\\
\\
After you are done setting the right options, you can generate a \textbf{controller} by using \textsl{ControllerConfig}'s \textsl{createController} method. All further interactions with your simulation are done through this controller.\\
\\
As a short example, this configuration would give you a Classic DEVS named \texttt{foosim} that saves every 8 cycles:
\begin{verbatim}
ControllerConfig conf = ControllerConfig();
conf.name = "foosim";
conf.saveInterval = 8;

@@

\section{Control}
You can choose to let the simulation end at a certain moment by adding a \textbf{termination time} or a \textbf{termination condition}.\\
The termination time can be set using the controller's \textsl{setTerminationTime} method, the termination condition by using \textsl{setTerminationCondition} and passing a custom \textsl{TerminationFunctor}.\\ %TODO add manual terminationfunctor?
\\
Finally, you can start the DEVS using the controller's \textsl{simulate} method.
%TODO Serializatie: save, load

>>>>

	The default is \emph{Classic DEVS}
\\\\
\end{tabular}
\\
\begin{tabular}{lp{8cm}}
\textit{simType} & The behavior of the Parallel DEVS:

	\begin{tabular}{l|l}
	\textsf{Option} & \textsf{Meaning} \\
	\texttt{OPTIMISTIC} & \emph{Optimistic PDEVS Simulation} \\
	\texttt{CONSERVATIVE} & \emph{Conservative PDEVS Simulation} \\
	\end{tabular} \newline

	The default is \emph{OPTIMISTIC} \newline
	\textit{[This option is disregarded if you do not run PDEVS]}
\\\\
\textit{coreAmount} & The amount of cores the simulation will run on \newline
						\textit{[This option is disregarded if you do not run PDEVS]} \newline
						By default this is 1
\\\\
\textit{saveInterval} & This value decides how often the simulation is saved and the tracing output dumped. A value of 3 would mean that this happens every 3 simulation cycles. \newline
						The default value is 5
\\\\
\textit{allocator} & By default this is the included \textsl{SimpleAllocator}
\\\\
\end{tabular}\\
\\
After you are done setting the right options, you can generate a \textbf{controller} by using \textsl{ControllerConfig}'s \textsl{createController} method. All further interactions with your simulation are done through this controller.\\
\\
As a short example, this configuration would give you a Classic DEVS named \texttt{foosim} that saves every 8 cycles:
\begin{verbatim}
ControllerConfig conf = ControllerConfig();
conf.name = "foosim";
conf.saveInterval = 8;

@@

\section{Control}
You can choose to let the simulation end at a certain moment by adding a \textbf{termination time} or a \textbf{termination condition}.\\
The termination time can be set using the controller's \textsl{setTerminationTime} method, the termination condition by using \textsl{setTerminationCondition} and passing a custom \textsl{TerminationFunctor}.

\subsection{Events}
If you want to schedule certain events while the simulation is running, like pausing and saving, you can use the Controller's \textsl{addPauseEvent} and \textsl{addSaveEvent} methods.\\
\\
The \textsl{addPauseEvent} method requires the \emph{simulated time} at which the simulator has to pause and how long the pause should take (in seconds).\\
The \textsl{addSaveEvent} method requires the \emph{simulated time} at which the simulation has to be saved and the \textsl{prefix} of the saved file. For example: a save at the simulated time \textit{100} with the prefix \texttt{mySimSave} will result in a file \texttt{mySimSave\_100.devs}.

For both events, the boolean value \textit{true} can be added as an additional argument to make the event repeat itself until the simulation ends.

\subsubsection{Loading a previous simulation}
Loading a previous simulation from a savefile follows the same procedure as setting up a regular simulation for the most part. First the simulation is configured (optionally by using the ControllerConfig object as described above), then instead of loading a new model, you can use the Controller's \textsl{load} method to load the data of your previous simulation.\\
\emph{Important: To load a simulation \textbf{do not} have to use the same configuration!}

\section{Starting the simulation}
Finally, you can start the DEVS using the controller's \textsl{simulate} method.
